---
title: "02-Circus Show"
date: 18.03.22
output:
 xaringan::moon_reader:
   yolo: true

---

```{r, echo=FALSE, include=FALSE}
library(babynames)
library(tidyverse)
```

# Introduce Yourself! 

> My name is Bethany and I am an Assistant Psychologist (Research) at BERRI Ltd. I live in Colchester with my Mum and Brother.

---

# Find me at...

All the details... 

---
class: center, middle

# Slide with centered content in the middle


My name is Beth.

--
 
I like sunshine.

--

seeing my friends,

--

and statistics.

---

.pull-left[
I also like the beach
![](Beachimage.jfif)
]

--

.pull-right[
and I have always wanted to visit a rainforest
![](Rainforest Image.jfif)
]

---

Hello Plot 

.pull-left[

```{r practice plot, fig.retina=3, echo=FALSE, include=TRUE}
library(babynames)
library(tidyverse)
tx_names <- babynames %>%
  filter(name == "Dallas" | name == "Austin") %>%
  filter(sex == "F")
name_plot <- ggplot(tx_names ,
                    aes(x= year,
                        y= prop,
                        group= name,
                        colour= name)) +
  geom_line()
name_plot

                    
```
]

.pull-right[

```{r include= TRUE, eval=FALSE}

tx_names <- babynames %>%
  filter(name == "Dallas" | name == "Austin") %>%
  filter(sex == "F")
tx_plot <- ggplot(tx_names ,
                    aes(x= year,
                        y= prop,
                        group= name,
                        colour= name)) +
  geom_line()
tx_plot
```

]

---
 
# A random slide to try out presenter notes. 

???

_you would say something extra here that you don't have in your slide_
